Estimation of flow trajectories in a multi-lines transportation network

### 2023-02-22 latex_files/applied_network_science_article/article_v0.tex
add graph to latex

The main goal of toy examples, since we have access to the real transportation flow, is to study how the resulting $MTE$ behave regarding passenger $st$-trips distribution and hyperparameter $\theta$ on different network sizes.

\begin{figure}
	\includegraphics[width=0.47\textwidth]{fig/toy_MTE_passengers_theta01.pdf}
	\includegraphics[width=0.47\textwidth]{fig/toy_MTE_tours.pdf}
	\caption{\emph{Mean transportation error} (MTE), according to the number of tours $p \in \{2,3,4,5,6,7,8\}$ and resp. to the number of passengers into the network per line tour and the minimum proportion $\theta =0.1$ of passengers entering/leaving the network at each stop with a proportional number of passengers to the shortest paths of each line tour.}
	\label{toy_MTE}
\end{figure}

>>>>

The main goal of toy examples, since we have access to the real transportation flow, is to study how the resulting $MTE$ behave regarding passenger $st$-trips distribution and hyperparameter $\theta$, on different network sizes. The randomness of the $st$-trips distribution

\begin{figure}
	\includegraphics[width=0.98\textwidth]{fig/MTE_passengers_theta01.pdf}
	\caption{\emph{Mean transportation error} (MTE), according to the number of tours $p \in \{2,3,4,5,6,7,8\}$ and resp. to the number of passengers into the network per line tour and the minimum proportion $\theta =0.1$ of passengers entering/leaving the network at each stop with a proportional number of passengers to the shortest paths of each line tour.}
	\label{MTE_vs_passengers}
\end{figure}

\begin{figure}
	\includegraphics[width=0.98\textwidth]{fig/MTE_tours.pdf}
	\caption{\emph{Mean transportation error} (MTE), according to the number of tours $p \in \{2,3,4,5,6,7,8\}$ and resp. to the number of passengers into the network per line tour and the minimum proportion $\theta =0.1$ of passengers entering/leaving the network at each stop with a proportional number of passengers to the shortest paths of each line tour.}
	\label{MTE_vs_theta}
\end{figure}
